### 2024-01-31 README.Rmd
update readme

## Processing detections

<!-- 1.  Process and tabulate the annotations. -->

```{r, eval=FALSE}
detections <- rofcamtrap::process_detections(
  input_dir = "2_LabelStudio/0_inputs/")
saveRDS(detections, "data/objects/detections.rds")
```

## Processing annotations

1.  Process and tabulate the annotations.

```{r, eval=FALSE}
annotations <- rofcamtrap::process_annotations(
   input_dir = "2_LabelStudio/2_outputs_processed/")

saveRDS(annotations, "data/objects/annotations_wide_treated.rds")

# Filter for non empty images
annotations_noempty <- annotations |>
  dplyr::filter(!is.na(to_name))

saveRDS(annotations_noempty, "data/objects/annotations_wide_noempty.rds")
```

@@

We need to download the models... TBA

### False detections classifier

@@

````{=html}
<!--
### Licenses

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> 
-->
````

>>>>

## Processing detections & annotations

See the quarto documents in the analysis directory.

@@

We need to download the models... TBC.

<!--
### False detections classifier

@@

### Licenses

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx> 
````
-->
